### 2017-05-29 doc/response.tex

- In terms of clarity, I would appreciate a better description of the
  IMAGINET model, which is being analyzed. The model is described in
  terms of its equations, but I would like to see a better
  presentation of what is the intent behind it -

- what is being modeled and what is being learned? this is available
  in the original IMAGINET paper, but I think the description should
  be imported to this paper also, in order to make it self contained
  and stronger.

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}
We have expanded Section~\ref{sec:imaginet} with a conceptual
description of {\sc Imaginet} and its learning goals, and added a graphical
representation of the structure of the model for more clarity (Figure~\ref{fig:imaginet}).
\end{quote}
\begin{verbatim}

- Also in terms of clarity, the graphs are not described in enough
  detail in my view. Whiel the box plots (figure 2 and others) are
  somewhat standard, they are not mainstream in the NLP commuity, and
  I would appreciate seeing a more detailed description in the main
  text or the caption of what each component means, both generally and
  in the context of the specific graph.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{explain the updated graph}
\end{quote}
\begin{verbatim}
- Figure 7 is confusing -- what are the different colors between,
  e.g., the words "in" and "tree" in the first line, and between "a"
  and "wii" in the second? I assume this is some "gradient" between
  two colors, but it looks like there are several data points and is
  very confusing. Please fix this.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  Following the recommendation of the reviewers,
we shortened Section~\ref{sec:micro} and removed this figure.
\end{quote}
\begin{verbatim}

@@

In terms of content:

- In section 6.1, why is the sorting by magnitude and not by absolute
  value? are negative activations not important?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  It is in fact the absolute value of the activations 
that is taken into account. We have changed the description of the top-k-contexts 
method to clear this issue.
\end{quote}
\begin{verbatim}

- When choosing the "top k context of each unit" (section 6.1), it is
  not clear what a "unit" is and how it is chosen.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  A unit is one neuron in the final hidden layer 
of the network. We have made this clear in the revised text.
\end{quote}
\begin{verbatim}

- I did not understand the last sentence in section 6.1, and would
  appreciate an elaboration on this point (or a removal).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We removed that sentence and added an expanded discussion of the generalizability of our techniques to the last section.
\end{quote}
\begin{verbatim}

- In section 6.2, it is not clear how trigrams with high activations
  are chosen. How is a trigram with high activation defined? this is
  not clear from the description of the method.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} \todo[inline]{This needs explanation and I don't have an answer (yet).}
\end{quote}
\begin{verbatim}

- I am not convinced by the experiments in section 6.3 and their
  importance -- either they are not described properly and I missed
  something, or they are somewhat meaningless: when training a
  logistic regression model to predict grammatical function, it is not
  surprising that ones finds units that are predictive of grammatical
  function.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have reorganized Section~\ref{sec:micro} and 
tried to motivate this particular experiment better. The idea is to 
come up with techniques for singling out units with a specific type
of function, such as encoding grammatical function. Therefore we 
use the coefficients of the logistic regression model as pointers 
to units of this type.
\end{quote}
\begin{verbatim}

@@

~ Where is section 6.4?

\end{verbatim}  
\begin{quote}
\textsc{Author Response:} It was there, believe us! But we have reorganized 
Section~\ref{sec:micro} and removed this experiment for the sake of clarity.
\end{quote}
\begin{verbatim}

@@

~ a related (unpublished, but available on arxiv) work is
https://arxiv.org/abs/1608.04207

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have expanded the discussion of related work 
(Section~\ref{sec:related}) and included this work in addition to a few others which 
came out while our submission was under review.
\end{quote}
\begin{verbatim}

@@

Revisions to be Encouraged:
:

5 Minor Revisions Required [Help]
:

See the points marked with (-) in the weaknesses above. Points marked
with (~) are less important. For section 6.3, my recommendation is
that it is either substantially revised, or removed altogether -- I
believe the paper has enough merit without it.

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We hope we have addressed all your comments and concerned. We did not remove the experiments in Section 6.3, but as we mentioned before we rewrote and restructured Section~\ref{sec:micro} and tried to put this experiment in context and clear our motivation.
\end{quote}
\begin{verbatim}

@@

Strengths:
: 
* neat idea and novel contribution (pairing activations with POS and
dependency relations to gain further insights into RNNs)

* extensive analysis; especially going beyond lexical cues (Section
5.3), where the authors train a regression model to predict omission
scores on a token level, showing that the network not just learns to
rely on word types, but it also learns position information
(particularly important for the textual pathway)

Weaknesses:
: 
* the description of the top K contexts is not clear, how are top k
contexts calculated? do you find the most active token (highest
absolute value of hidden activation in the sequence?) and then use
the words around it to find the trigrams? (what is meant by 'each
unit' in Section6.1? Is the matrix actually R^nxd?); maybe you sort
by column, not row?

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  You are absolutely right about the description of 
the top-k-context method being confusing. We have rewritten this part to make the description of the method more clear. Furthermore, we have reorganized 
Section~\ref{sec:micro} to make it more coherent. 
\end{quote}
\begin{verbatim}

@@

* Section 6.5 shows that the visual pathway focuses more on dependency
relations, supporting the finding in the omission score part;
however, the section is again very dense and Figure 7 only shows
activations for Visual; I'd suggest to drop this part from the paper

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  Following your and others' suggestion, we have removed this section from the revised manuscript.
\end{quote}
\begin{verbatim}

@@

4 Substantive Revisions Required [Help]

Complete this section if either 'Revise and Resubmit' or 'Reject' has
been recommended.

Revisions to be Required:
: 
- clearer description of how top k contexts are obtained
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  As mentioned above, we have rewritten Section~\ref{sec:micro} to make the description of the methods and the experiments more clear.
\end{quote}
\begin{verbatim}

@@

3 Strengths and Weaknesses [Help]

Strengths:
: 
This paper makes a useful methodological contribution by proposing
methods to analyze the knowledge learned by neural networks, which is
an underexplored area, at least for networks trained on text data. The
paper is well written, and technically sound.

Weaknesses:
: 
The results of the paper are unfortunately fairly obvious. From the
omission score analysis, we learn that a model trained to predict the
next word in a sentence is sensitive to function words, while a word
trained to associate a sentence with an image representation (which is
essentially the output of the object detector) pays more attention to
nouns. This is not at all surprising, it just reflects the different
training objectives. The fact that the hidden units respond to
specific n-grams is also expected; most people already believe that
RNNs are good at approximating n-gram models; the question is, can
they model more elaborate syntactic structures?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{address}
\end{quote}
\begin{verbatim}

This is really the question that the authors should explore, e.g., by
testing whether the model can learn long distance dependencies,
agreement, recursion, word order. An example for recent work that goes
in this direction is Linzen et al. (2016).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We have expanded the related work 
(Section~\ref{sec:related}) with a discussion of Linzen et al. (2016) 
and a few other articles that came out while our submission was under review.
\end{quote}
\begin{verbatim}

@@

(2) Add comparisons to other architectures (LSTMs, etc.)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{hmm.}
\end{quote}
\begin{verbatim}

(3) Sec. 5.3.2 should be cut. You don't have connected discourse, just
isolated sentences. So it is purely speculative to say these
observations are due to topic/content structure, rather than just to
linear order.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{explain the rewritten version.}
\end{quote}
\begin{verbatim}

(4) The paper relies too much on impressionistic evaluation based on
suggestive figures, rather than on quantitative analysis. An exception
is Fig. 8. There should be more of this type of analysis.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{address.}
\end{quote}
\begin{verbatim}

(5) The authors should discuss the recent paper by Linzen et
al. (2016). This is a good example for an attempt to evaluate
linguistic structure learned by an RNN that goes beyond individual
words or n-grams.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  As mentioned before, we have included a discussion of
this paper in our related work.
\end{quote}
\begin{verbatim}

### 2017-05-29 doc/response.tex

Complete this section if either 'Revise and Resubmit' or 'Reject' has
been recommended.

Revisions to be Required:
: 
- clearer description of how top k contexts are obtained
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  As mentioned above, we have rewritten Section~\ref{sec:micro} to make the description of the methods and the experiments more clear.
\end{quote}
\begin{verbatim}

Revisions to be Encouraged:
: 
- figures are not readable in BW printing; in addition to color, use
  different symbols/line types
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{update graphs?}
\end{quote}
\begin{verbatim}

- Related Work: clarify better how you differ from Li et al. (2015),
  you mention "for a comparative analysis": I interpret this as "we
  analyze a multi-task learning model (visual / textual) and compare
  what the two parts learn"
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We have edited our related work section to make the comparison more 
clear. In addition to taking into account tasks that rely on different modalities (language as well as vision), 
we focus more on learning structural properties of the input, whereas Li et al. (2015) focus on single
tokens.
\end{quote}
\begin{verbatim}

### 2017-05-29 doc/categories.tex
Mostly adding stuff about LM

%\subsection{Salience of categories of words}
%\label{sec:salience}
In this section we propose novel techniques for interpreting the
activation patterns of neural networks trained on language tasks
from a linguistic point of view and focus
on the high level understanding of what parts of input sentence the networks
pay most attention to. Furthermore, we investigate if the networks
learn to assign differential amounts of importance to tokens depending
on their position and grammatical function in the sentences.\label{edit:whyposdep}
In Section \ref{sec:computeomission} we introduce \emph{omission scores};
a metric to measure the contribution of each token to the prediction of the networks.
Section \ref{sec:omitimaginet} aggregates the omission scores in terms
of dependency relations and part-of-speech categories and compares {\sc Visual}
and {\sc Textual}. Section \ref{sec:beyondlexical} investigates the extent to which
the importance of words for the different networks depend on the words themselves,
their position and their grammatical function in the sentences.
% MAYBE THIS WOULD BE TOO MUCH
%We apply the proposed methods to explore
%the representations of {\sc Imaginet}, but also discuss how to generalize
%them to other architectures.

@@

In both pathways of {\sc Imaginet} the full sentences are represented by the
activation vector at the end-of-sentence symbol
($\mathbf{h}_\text{end}$). We measure the salience of each word $S_i$
in an input sentence $S_{1:n}$ based on how much the representation of the
partial sentence $S_{\setminus i} = S_{1:i-1}S_{i+1:n}$, with
the omitted word $S_i$, deviates from that of the original sentence
representation. For example, the distance
between $\mathbf{h}_\text{end}(${\it the black dog is running}$)$
and $\mathbf{h}_\text{end}(${\it the dog is running}$)$ determines
the importance of {\it black} in the first sentence. We introduce the
measure $\mathrm{omission}(i,S)$ for estimating the salience of a word $S_i$:

@@

\noindent Figure~\ref{fig:omissionex} demonstrates the omission
measure for the {\sc Visual} and {\sc Textual} pathways for two
example captions. For both captions the $\mathrm{omission}$ scores are
plotted along with the first image retrieved by {\sc Visual} for the
full sentence and for the sentence with the word with the highest
$\mathrm{omission}(i,S)$ removed. The images are retrieved from the
validation set of MS-COCO by: 1) computing the image representation of the 
given sentence with {\sc Visual}; 2) extracting the CNN features for the 
images from the set; and 3) finding the image that minimizes the cosine distance
to the query.\label{edit:retrievalexplain} 
In the first example, the omission
scores for {\sc Visual} suggest that the model interpreted {\it  pizza} as the most important
word in the sequence and returned an image that depicts a pizza on a plate. 
Removing the word {\it pizza} promotes {\it salad} and {\it bowl} as
the main theme of the sentence and the model retrieves an image with a dining table 
with salad-like dishes. 
For the second example, the omission scores for {\sc
  Visual} show that the model paid attention mostly to {\it baby} and
{\it bed} and slightly to {\it laptop} and retrieved an image depicting a baby 
sitting on a bed with a laptop.
Removing the word {\it baby} leads
to an image that depicts an adult male laying on a bed. Figure~\ref{fig:omissionex}
also shows that in contrast to {\sc Visual}, in both examples {\sc
  Textual} distributes its attention more evenly across time steps
instead of focusing on the types of words related to the corresponding
visual scene.

For other RNN architectures such as GRUs, LSTMs \label{edit:omitgeneral}
and their bi-directional variants, measuring the contribution
of tokens to their predictions the $\mathrm{omission}$ 
can be straight-forwardly computed using their hidden state 
at the last time step used for prediction. Furthermore, the technique 
can be applied in general to other architectures which
embed variable length linguistic expressions to the same fixed dimensional
space and perform predictions based on these embeddings. 
This includes tree-structured Recursive Neural Network models such as the Tree-LSTM
introduced in \namecite{kai2015treelstm} or the CNN architecture of \namecite{yoonneural2014} 
for sentence classification. In both cases the pre-softmax activations can be extracted 
from the models as the representations of the full and partial sentences.

@@

\caption{Distribution of omission scores for POS (left) and dependency labels
  (right), for the {\sc Textual} and {\sc Visual} pathways. Only labels which occur at least 500 times are included.}
\label{fig:omission-imaginet}
\end{figure*}

@@

\begin{figure*}[t]
  \centering
  \hspace*{-0.2in}
  \setlength{\tabcolsep}{0pt}
  \begin{tabular}{cc}
  \includegraphics[scale=0.55]{imaginet-omission-quotient-pos-boxplot.png} &
  \includegraphics[scale=0.55]{imaginet-omission-quotient-dep-boxplot.png} \\  
  \end{tabular}
  \caption{Distributions of log ratios of omission scores of {\sc LM} to {\sc Textual} per
    POS (left) and dependency labels (right). Only labels which occur at least 500 times are included.}
\label{fig:omission-imaginet-ratio}
\end{figure*}

The $\mathrm{omission}$ scores can be used not only to
estimate the importance of individual words, but also of syntactic
categories. We estimate the salience of each syntactic category by
accumulating the omission scores for all words in that category. We
tag every word in a sentence with the part-of-speech (POS) category
and the dependency relation (deprel) label of its incoming arc. For
example, for the sentence \emph{the black dog}, we get ({\it
  the},~DT,~det), 
({\it black},~JJ,~amod), ({\it dog},~NN,~root). 
Both POS tagging and dependency parsing are performed jointly
using the TurboParser dependency parser \cite{martins2013turning}.\footnote{Available at
  \url{https://github.com/andre-martins/TurboParser}{github.com/andre-martins/TurboParser}.} The POS tags used are the Penn Treebank tags and the dependencies are 
the Stanford basic dependencies.

Figure~\ref{fig:omission-imaginet} shows the distribution of omission
scores per POS and deprel label for the two pathways of {\sc Imaginet}. 
The general trend is that for the {\sc Visual} pathway, the omission scores are
high for a small subset of labels - corresponding mostly to nouns, less so for
adjectives and even less for verbs - and low for the rest (mostly function words and
various types of verbs). For {\sc Textual} the differences are \label{edit:textualomission}
smaller, and the pathway seems to be sensitive to the omission of most
types of words.

Figure~\ref{fig:omission-imaginet-ratio} compares the
two pathways directly using the log of the ratio of the {\sc Visual}
to {\sc Textual} omission scores, and plots the distribution of this
ratio for different POS and deprel labels.  Log ratios above zero
indicate stronger association with the {\sc Visual} pathway and below
zero with the {\sc Textual} pathway. We see that in relative terms,
{\sc Visual} is more sensitive to nouns (NNP, NNS, NN), numerals (CD)
and adjectives (JJ), and {\sc Textual} to the prepositions (TO, IN),
some types of verbs (VBZ, VBP), determiners (DET, WDT) and
particles (RP). This picture is complemented by the analysis of the
relative importance of dependency relations: {\sc Visual} pays most
attention to the relations {\sc nsubjpass, nsubj, pobj, root, dobj,
  nn, conj, dep, amod} and {\sc num}, whereas {\sc Textual} is more
sensitive to {\sc det, mark, aux, auxpass, prt, prep, poss, cc} and
{\sc cop}.

As expected, {\sc Visual} is more focused on grammatical
functions typically filled by semantically contentful words, while
{\sc Textual} distributes its attention more uniformly and 
attends relatively more to purely grammatical functions. 
It is worth noting, however, the relatively low omission scores for verbs in case \label{edit:generality}
of {\sc Visual}. One might expect that the task of image prediction from
descriptions requires general language understanding and so high omission
scores for all content words in general, however, the results
suggest that this setting is not optimal for learning useful representations of verbs,
which possibly leads to representations that are too task specific 
and not transferable across tasks.

>>>>

%\subsection{Salience of categories of words}
%\label{sec:salience}
In this section we propose novel techniques for interpreting the
activation patterns of neural networks trained on language tasks
from a linguistic point of view and focus
on the high level understanding of what parts of input sentence the networks
pay most attention to. Furthermore, we investigate if the networks
learn to assign differential amounts of importance to tokens depending
on their position and grammatical function in the sentences.\label{edit:whyposdep}
In Section~\ref{sec:computeomission} we introduce \emph{omission scores};
a metric to measure the contribution of each token to the prediction
of the networks and in Section~\ref{sec:omitimaginet} we analyze how
these scores are distributed over dependency relations and
part-of-speech categories. 
In Section~\ref{sec:beyondlexical} we investigate the extent to which
the importance of words for the different networks depend on the words themselves,
their sequential position and their grammatical function in the sentences.
% MAYBE THIS WOULD BE TOO MUCH
%We apply the proposed methods to explore
%the representations of {\sc Imaginet}, but also discuss how to generalize
%them to other architectures.

@@

In all the models the full sentences are represented by the
activation vector at the end-of-sentence symbol
($\mathbf{h}_\text{end}$). We measure the salience of each word $S_i$
in an input sentence $S_{1:n}$ based on how much the representation of the
partial sentence $S_{\setminus i} = S_{1:i-1}S_{i+1:n}$, with
the omitted word $S_i$, deviates from that of the original sentence
representation. For example, the distance
between $\mathbf{h}_\text{end}(${\it the black dog is running}$)$
and $\mathbf{h}_\text{end}(${\it the dog is running}$)$ determines
the importance of {\it black} in the first sentence. We introduce the
measure $\mathrm{omission}(i,S)$ for estimating the salience of a word $S_i$:

@@

\noindent Figure~\ref{fig:omissionex} demonstrates the omission
measure for the {\sc LM}, {\sc Visual} and {\sc Textual} networks for an
example captions. The $\mathrm{omission}$ scores are
plotted for the
full sentence and for the sentence with the word with the highest
$\mathrm{omission}(i,S)$ removed. 
Figure~\ref{fig:omissionexpic} shows the images retrieved by {\sc
  Visual} for the full
caption and for the one with the word {\sc baby} omitted. 
The images are retrieved from the validation set of MS-COCO by: 1)
computing the image representation of the given sentence with {\sc
  Visual}; 2) extracting the CNN features for the images from the set;
and 3) finding the image that minimizes the cosine distance to the
query.\label{edit:retrievalexplain} 
The omission scores for {\sc Visual} show that the model paid attention
mostly to {\it baby} and {\it bed} and slightly to {\it laptop} and
retrieved an image depicting a baby sitting on a bed with a laptop.
Removing the word {\it baby} leads to an image that depicts an adult
male laying on a bed. Figure~\ref{fig:omissionex} also shows that in
contrast to {\sc Visual}, {\sc Textual} distributes
its attention more evenly across time steps instead of focusing on the
types of words related to the corresponding visual scene. The peaks
for {\sc LM} are the same as for {\sc Textual}, but the variance of
the omission scores is higher, suggesting that the unimodal language
model is more sensitive overall to input perturbations than {\sc Textual}.

For other RNN architectures such as LSTMs \label{edit:omitgeneral}
and their bi-directional variants, measuring the contribution
of tokens to their predictions the $\mathrm{omission}$ 
can be straight-forwardly computed using their hidden state 
at the last time step used for prediction. Furthermore, the technique 
can be applied in general to other architectures which
embed variable length linguistic expressions to the same fixed dimensional
space and perform predictions based on these embeddings. 
This includes tree-structured Recursive Neural Network models such as the Tree-LSTM
introduced in \namecite{kai2015treelstm} or the CNN architecture of \namecite{yoonneural2014} 
for sentence classification. In both cases the pre-softmax activations can be extracted 
from the models as the representations of the full and partial sentences.

@@

\caption{Distribution of omission scores for POS (left) and dependency labels
  (right), for the {\sc Textual} and {\sc Visual} pathways and for
  {\sc LM}. Only labels which occur at least 500 times are included.}
\label{fig:omission-imaginet}
\end{figure*}

@@

The $\mathrm{omission}$ scores can be used not only to
estimate the importance of individual words, but also of syntactic
categories. We estimate the salience of each syntactic category by
accumulating the omission scores for all words in that category. We
tag every word in a sentence with the part-of-speech (POS) category
and the dependency relation (deprel) label of its incoming arc. For
example, for the sentence \emph{the black dog}, we get ({\it
  the},~DT,~det), 
({\it black},~JJ,~amod), ({\it dog},~NN,~root). 
Both POS tagging and dependency parsing are performed 
using the  dependency parser from the Spacy package.\footnote{Available at
  \url{https://spacy.io/}.} 
%The POS tags used are the Penn Treebank tags and the dependencies are 
%the Stanford basic dependencies.

Figure~\ref{fig:omission-imaginet} shows the distribution of omission
scores per POS and dependency label for the two pathways of {\sc
  Imaginet} and for {\sc LM}.  The general trend is that for the {\sc
  Visual} pathway, the omission scores are high for a small subset of
labels - corresponding mostly to nouns, less so for adjectives and
even less for verbs - and low for the rest (mostly function words and
various types of verbs). For {\sc Textual} the differences
are \label{edit:textualomission} smaller, and the pathway seems to be
sensitive to the omission of most types of words.  For {\sc LM} the
distribution over categories is also relatively uniform, but the omission scores are higher
overall than for {\sc Textual}.

Figure~\ref{fig:omission-imaginet-ratio} compares the two pathways of
{\sc Imaginet} directly using the log of the ratio of the {\sc Visual}
to {\sc Textual} omission scores, and plots the distribution of this
ratio for different POS and dependency labels.  Log ratios above zero
indicate stronger association with the {\sc Visual} pathway and below
zero with the {\sc Textual} pathway. We see that in relative terms,
{\sc Visual} is more sensitive to adjectives (JJ), nouns (NNS, NN) and
numerals (CD), and {\sc Textual} to the prepositions (TO, IN),
determiners (DT, WDT) and pronouns (PRP) as well as some types of
verbs (VBZ, VBP).

This picture is complemented by the analysis of the
relative importance of dependency relations: {\sc Visual} pays most
attention to the relations {\sc nsubjpass, attr, amod, nsubj, ROOT,
  compound, dobj, nummod}
whereas {\sc Textual} is more sensitive to {\sc det, mark, prep, aux,
  auxpass, cc, poss, advmod, prt, relcl}.
As expected, {\sc Visual} is more focused on grammatical
functions typically filled by semantically contentful words, while
{\sc Textual} distributes its attention more uniformly and 
attends relatively more to purely grammatical functions.

It is worth noting, however, the relatively low omission scores for verbs in case \label{edit:generality}
of {\sc Visual}. One might expect that the task of image prediction from
descriptions requires general language understanding and so high omission
scores for all content words in general, however, the results
suggest that this setting is not optimal for learning useful representations of verbs,
which possibly leads to representations that are too task specific 
and not transferable across tasks.

\begin{figure*}[t]
  \centering
  \hspace*{-0.2in}
  \setlength{\tabcolsep}{0pt}
  \begin{tabular}{cc}
  \includegraphics[scale=0.55]{imaginet-omission-quotient-pos-boxplot.png} &
  \includegraphics[scale=0.55]{imaginet-omission-quotient-dep-boxplot.png} \\  
  \end{tabular}
  \caption{Distributions of log ratios of omission scores of {\sc LM} to {\sc Textual} per
    POS (left) and dependency labels (right). Only labels which occur at least 500 times are included.}
\label{fig:omission-imaginet-quotient}
\end{figure*}

Figure~\ref{fig:omission-imaginet-quotient} shows a similar analysis
contrasting {\sc LM} with the {\sc Textual} pathway of {\sc
  Imaginet}. The first observation is that the range of values of the
log ratios is narrow, indicating that the differences between these
two networks regarding which grammatical categories they are sensitive
to is less pronounced than when comparing {\sc Visual} to {\sc
  Textual}. While the size of the effect is weak, there also seems to
be a tendency for the {\sc Textual} model to pay relatively more
attention to lexical and less to structural dependencies, compared to
{\sc LM}: it may be that the {\sc Visual} pathway pulls {\sc Textual}
in this direction by sharing word embeddings with it.

### 2017-05-29 doc/experiments.tex
Mostly adding stuff about LM

In the following sections, we report a series of experiments in which
we explore the kinds of linguistic regularities the
{\sc Textual} and {\sc Visual} pathways of {\sc Imaginet} learn from
word-level input. Section~\ref{sec:macro} presents the macro-level
analyses where we propose methods to analyze the final hidden activation 
vectors of the recurrent pathways from linguistic point of view. 
Section~\ref{sec:micro} reports exploratory experiments on
the linguistic features encoded by individual hidden units. 
In both sections we report our findings based on the {\sc Imaginet} model
and discuss the generalizabilty of our methods to other architectures.
\label{edit:experimentsgeneral}
For all the experiments, we trained {\sc Imaginet} on the training portion of the
MSCOCO image-caption dataset \cite{lin2014microsoft}, and analyzed the
representations of the sentences in the validation set. The target
image representations were extracted from the pre-softmax layer of the
16-layer CNN of \namecite{simonyan2014very}.

>>>>

In the following sections, we report a series of experiments in which
we explore the kinds of linguistic regularities the
networks learn from
word-level input. Section~\ref{sec:macro} presents the macro-level
analyses where we propose methods to analyze the final hidden activation 
vectors of the recurrent pathways from linguistic point of view. 
Section~\ref{sec:micro} reports exploratory experiments on
the linguistic features encoded by individual hidden units. 
In both sections we report our findings based on the {\sc Imaginet}
model, discuss the generalizabilty of our methods to other architectures.
\label{edit:experimentsgeneral}, and whenever appropriate compare to
our two other models, {\sc LM} and {\sc Sum}.  For all the
experiments, we trained {\sc Imaginet} on the training portion of the
MSCOCO image-caption dataset \cite{lin2014microsoft}, and analyzed the
representations of the sentences in the validation set corresponding
to 5000 randomly chosen images. The target image representations were
extracted from the pre-softmax layer of the 16-layer CNN of
\namecite{simonyan2014very}.
